\documentclass[11pt]{article}
\input{misc_mac}
\input{macros}
\begin{document}
I have a rigid body in a fluid modeled by SPH. What are its equations 
of motion. 

First we start with kinematics. 

I would like the model to rotate with angular speed $\omgvec$, where the 
boldface character represents an axis of rotation. The axis passes
through the point $x_P$.  We will generalize later. Assume this rigid
object is formed from a collection of points $x_i$ that do not move 
relative to each other. In other words: $(x_i-x_j)\cdot(x_k-x_l)$ is 
constant for all time and for all $i,j,k,l$. 

First assume that $\omgvec$ is independent of time (constant angular
velocity and constant axis of rotation).
$$
\vvec_R = \vvec_{cg} + \omgvec \times \rvec_R
$$
where $\vvec_R$ is the velocity of point $R$ on the rigid body, the 
subscript $cg$  denotes center of gravity of the rigid body, 
and $\rvec_R$ is a vector from the center of gravity to the point $R$. 
Now apply this equation to compute the velocity (in the lab frame of 
reference) of particle $S$ on the rigid body: 
$$
\vvec_S = \vvec_{cg} + \omgvec \times \rvec_S
$$
Subtract the two equations: 
$$
\vvec_R-\vvec_S = \omgvec \times (\rvec_R-\rvec_S)
$$
If point $S$ is stationary in the laboratory frame of reference, 
$\vvec_S=0$ and
$$
\vvec_R = \omgvec \times (\rvec_R-\rvec_S) .
$$

To implement this, store the stationary point in a Point3.
and store the rotation vector in another Point3. 

Every iteration, compute the velocity of all the points. Do this on the 
with a GPU kernel: 

computeVel(int num, float4* pos_s, float4 omega, float4 pos_cg)
{
    r = pos_s[index] 
	v = omg x (r - pos_cg)
}

I have implemented the above. The boundaries are not treated very well. When the arm rotates against the fluid, I expect more waves, but the arm appears to be simply moving "through" the fluid with no force acting on the fluid. The BC modifies the force of the fluid
particle. Perhaps there should be more force away from the boundary. 
Also, there is an issue of moving the boundary at a different time from when the fluid particles are moving. So if the boundary is moving too fast relative to the fluid, the fluid
particle could go from one side of the boundary to the other in one time step. That is not good. Either the motion of the boundary would have to be reduced, or the time step reduced (not sure this time step decrease is valid).
----------------------------------------------------------------------

\end{document}
